---
title: "PSY 8960 final Project"
author: "Annie Griebie"
date: "`r Sys.Date()`"
output: html_document
---
## Script Settings and Resources
```{r script_settings_and_resources, message=FALSE}
setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
library(tidyverse)
library(ggplot2)
```

## Data Import and Cleaning
```{r data_import_and_cleaning, message=FALSE}
finaldata_tbl <- readRDS("../data/finaldata_tbl.RDS")
shiny_tbl <- finaldata_tbl %>% 
select(MonthlyIncome, Attrition, JobSatisfaction, Department, EducationField, Gender, JobRole) %>% mutate(Attrition = case_when(Attrition == "Yes" ~ 1, Attrition == "No" ~ 0)) %>%
saveRDS("../shiny/people_dashboard/shiny_input.RDS")
```

## Online Resources- Comment of link to app running on shinyapps.io
An interactive web app for this data is available by [clicking this link](https://anniepsy8960datascience.shinyapps.io/people_dashboard/)

## Explanation of Approaches
#First added selectInput option for users to select which of the variables they wanted to examine, or subset, within the histogram that would be created for visualization. For variables of a single column I created an "All" option for the default option. I chose to do these as options as selectInput options rather than using radioButtons because I thought it was more visually easy to understand having drop down options on the sidebar that then only showed what had been selected rather than having all possible options visible at once which I thought could ultimately be confusing.
#Next I created an output for the plot, the table below the plot that would include descriptive statistics. 
#In order to create the plot I used the selectInput options I had created in the first step to create a histogram for each of the three outcome variables of Monthly Pay, Turnover Status and Job Satisfaction. I changed the binwidth to be 500 to avoid the warning that occured within the console that stated that the bins were set to 30 and needed to reset the value.
#I then added a text output option to display under my table when the Turnover Status outcome variable was selected because in my skinny data table I had relabeled the Attrition variable to be numeric so that it could be called later for the descriptive statistics and used to calculate the mean and sd. Alternatively, I could have waited to convert the Attrition column until I was about to run the mean and sd functions however I was not sure it was appropriate to be relabeling columsn from the dataset in the shiny app document itself therefore chose to make the change prior to exporting the skinny data set used.
#Next I created the output table. I needed to group variables to call into table, tried creating a reactive function because according to "https://shiny.rstudio.com/tutorial/written-tutorial/lesson4/" a reactive output is useful for dynamically generating an automatic response with changing selections, when tried wrapping in reactive expression received an error code on app that table input needed to be a variable list, not sure if I wrapped the function incorrectly or if this is common. So used the append function instead to add the single variable element being selected into the grouping vector, I wwas then able to call these into the summarise function and use the mean and sd function to generate the descriptive statistics within the generated table. 